Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis.

### 2018-06-22 manuscript/03_results.Rmd
Minor tweaks to results and discussion text on Vcmax/Jmax

The strength of the correlations of $N$ with photosynthetic parameters $V_{c,max}$ and $J_{max}$ varied by plant functional type, regardless of whether the traits were normalized by mass or area.

>>>>

The strength of the correlations of $N$ with photosynthetic parameters $V_{c,max}$ and $J_{max}$ varied by PFT, regardless of whether the traits were normalized by mass or area.
